Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method

### 2019-09-12 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

\textit{Outline}. Section~\ref{sec:Background} gives the background about program synthesis, design sizing and validation of PV systems, and the mathematical modeling. Section~\ref{sec:Method} presents the automated formal synthesis proposed in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.

@@

Here we explain the adopted method to size stand-alone solar PV systems, and what type of criteria and technique is possible to apply for the optimal sizing.

@@

A PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required. The AC load dictates the behavior of AC electrical load from the house. % that will be fed by the PV system.

%The sizing check stage will ensure that the system meets the standard project steps related  to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice, among other sizing techniques and possibilities. 
Among the techniques that can be used for the sizing of PV systems, it was adopted here the critical period solar energy method~\cite{Pinho}, with the use of MPPT (Maximum Power Point Tracking) charge controller (which is the most common nowadays). Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PV Systems Optimization Criteria}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to select an optimal combination to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.

@@

%----------------------------------------------------------------------------------------------
\subsection{PV Systems Optimization Techniques}
%----------------------------------------------------------------------------------------------

In order to recommend an optimal configuration for PV systems, 
the designer has to evaluate the design based on optimization variables. 
As the number of optimization variables increases, the computational effort 
will increase as well. Hence, to obtain the best PV system design as well as 
simplified sizing process, prior work introduced three main techniques 
for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.

@@

Although simulation and testing explore possible behaviors and scenarios of a given system, 
they leave open the question of whether unexplored trajectories may contain a flaw. 
Formal verification conducts an exhaustive exploration of all possible behaviors; 
when a design is said to be ``correct'' by a formal verification method, it implies that all 
behaviors have been explored, and questions regarding adequate coverage or missed behavior 
becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
applies mathematical reasoning to obtain guarantees about the correctness of a system; 
one successful method in this domain is model checking~\cite{Clarke2012}. 
Here we use one state-of-the-art model checker, who was awarded with the Golden Medal at the annual competition in software verification~\cite{LMU2019}, to formally verifying PV designs w.r.t. user requirements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\textit{Outline}. Section~\ref{sec:Background} gives the background about sizing and optimization of PV systems. Section~\ref{sec:Method} presents the automated formal synthesis proposed in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, results and analysis. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.

@@

A stand-alone PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required. The AC load dictates the behavior of AC electrical load from the house. % that will be fed by the PV system.

In this section we explain the adopted method to size stand-alone solar PV systems, and what criteria and technique is possible to apply for the optimal sizing.

@@

At this work, was adopted the critical period solar energy method~\cite{Pinho}, and MPPT (Maximum Power Point Tracking) charge controller (which is the most common nowadays). Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PV Systems Optimization: Criteria and Techniques}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to select an optimal PV system to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives or \textbf{criteria}.

@@

Parallel to criteria, in order to recommend an optimal configuration for PV systems, 
the designer has to evaluate the design based on optimization variables. 
As the number of optimization variables increases, the computational effort 
will increase as well. Hence, to obtain the best PV system design as well as 
simplified sizing process, prior work introduced three main \textbf{techniques} 
for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.

@@

Although simulation and testing explore possible behaviors and scenarios of a given system, 
they leave open the question of whether unexplored trajectories may contain a flaw. 
Formal verification conducts an exhaustive exploration of all possible behaviors; 
when a design is said to be ``correct'' by a formal verification method, it implies that all 
behaviors have been explored, and questions regarding adequate coverage or missed behavior 
becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
applies mathematical reasoning to obtain guarantees about the correctness of a system; 
one successful method in this domain is model checking~\cite{Clarke2012}.

In order to perform the automated formal synthesis, we will use a state-of-the-art model checker, who was awarded with the Golden Medal at the annual competition in software verification~\cite{LMU2019}, the \textbf{CPAchecker}.
